\cleardoublepage

```{r echo=FALSE, results='asis'}
# This is the first appendix
if(!is_latex_output()){
  cat("# (APPENDIX) Appendix {-}")
} else {
  cat("\\appendix")
}
```


```{r setup_appA, include=FALSE}
chap <- "A"
lc <- 0
rq <- 0
# **`r paste0("(LC", chap, ".", (lc <- lc + 1), ")")`**
# **`r paste0("(RQ", chap, ".", (rq <- rq + 1), ")")`**
opts_chunk$set(
  tidy = FALSE, 
  out.width = '\\textwidth', 
  fig.height = 4,
  warning = FALSE
)
```


# Privacy {#privacy}

We need to cover two sorts of privacy: the privacy of those whose materials we verify, and your own privacy. There are limitations to both, but we attempt to protect privacy as much as possible.

##  Privacy of Replicators

You are tasked with reproducing articles. Much as referees for journals mostly remain anonymous, we want you to remain anonymous as well.

- You *may* reveal yourself to authors later (after the task is completed), if you wish. 
- You should *not* contact authors unless authorized by the Lab Leader. Normally, all such communications go through the Lab Leader.
- We do *name* you (to thank you) in the annual report, but do not attribute your work to any one article.
- In the empirical analysis of all the articles, we replace your netid and name with an anonymous (and untraceable) identifier. So we can track that you have done Articles A1, D57, and Z31, but nobody knows that it was **you**.

There is "leakage" of information:

- In order to download materials, you need to login to openICPSR, and have the ability to download from specific deposits. This *does* reveal your name to the depositors. This is currently a technological constraint, and cannot be avoided without great complications.
  - If you have concerns, please let us know, and we will find a workaround. 

Should you ever be contacted in some unacceptable fashion by authors, you should immediately contact the Lab Leadership. 

You can, and you **should**, reveal your affiliation with this project! You can (and you should) be proud of the work you will do or have done, and you are allowed (and you should) reference this project as an accomplishment.

## The Privacy of Authors

When we do pre-publication verification, this is equally important.

- You are never allowed to reveal that the author has submitted to the journal
  - This includes when you need to contact third parties for materials that are part of the replication materials. In case of doubt, contact Lab Leadership.
- You are never allowed to reveal anything about the analysis that the author is conducting, and that you are reproducing, to anybody outside of this group.
- You must never put the code, the article, or the data on a location where others outside of this group could access it
  - Bitbucket within the `aeaverification` project is OK, do not attempt to make a repository public (even if it may seem convenient not to have to enter your login etc.)
  - Remove the files from your  laptop as soon as you are done with it (after `git push`, of course)
  - You may remove them from CISER nodes, but those will be cleansed later
  - Do not email or otherwise disseminate (twitter, facebook, snapchat, whatever) the files received, or any other information about the papers

